Evaluation of pilot jobs for Apache Spark\\ applications on HPC clusters

### 2019-05-21 paper.tex
final fixes

In the case of pilots, multiple Slurm jobs, each with potentially different queuing times,
were used. Figure~\ref{fig:mwall} displays the makespan times for an average number of workers
given an experiment configuration, where the line corresponds to the estimated makespan using 
our performance model. Makespan for the model was calculated as:
$$
M = \frac{125\times(d + 20)}{W}\times 10,
$$
where:
\begin{itemize}
    \item $125$ is the number of chunks BigBrain was split into
    \item $M$ is the makespan of the application, in seconds
    \item $W$ is the average number of Spark workers throughout the execution, computed as in Equation~\ref{eq:avgw}
    \item $d$ is the task delay, in seconds, associated with a given configuration
    \item $20$ is the average measured incrementation duration, in seconds, for a BigBrain chunk
    \item $10$ is the number of iterations
\end{itemize}
As can be seen in the Figure~\ref{fig:mwall}, both pilots and batch 
followed the general trend denoted by the model, which confirms that 
the system was behaving without major external sources of
overhead. However, pilots were consistently slower than batch for the same
number of average workers. This is particularly visible in Configuration 4
on B\'eluga (Fig. \ref{fig:mwbeluga}), and in Configuration 2, 3 and 4 on
Cedar (Fig. \ref{fig:mwcedar}). It means that some sort of overhead
impacted pilots but not batch. It can also be noticed that both batch and
pilots occasionally deviated from the model line, in particular
Configurations 2 and 3 in B\'eluga: this is due to the fact that our
application is not a divisible load, as the model assumes. Extending the
model beyond divisible loads is easy enough for batch and confirms that the
observed deviations from the model line come from this assumption (see gray
line in Fig.~\ref{fig:mwall}). The extended expression for pilots is more complex
though.

>>>>

In the case of pilots, multiple Slurm jobs, each with potentially different queuing times,
were used. Figure~\ref{fig:mwall} displays the makespan times for an average number of workers
given an experiment configuration, where the coloured line corresponds to the estimated makespan using 
our performance model. Makespan for the model was calculated as:
$$
M = \frac{125\times(d + 20)}{W}\times 10,
$$
where:
\begin{itemize}
    \item $125$ is the number of chunks BigBrain was split into
    \item $M$ is the makespan of the application, in seconds
    \item $W$ is the average number of Spark workers throughout the execution, computed as in Equation~\ref{eq:avgw}
    \item $d$ is the task delay, in seconds, associated with a given configuration
    \item $20$ is the average measured incrementation duration, in seconds, for a BigBrain chunk
    \item $10$ is the number of iterations
\end{itemize}
As can be seen in the Figure~\ref{fig:mwall}, both pilots and batch 
followed the general trend denoted by the model, which confirms that 
the system was behaving without major external sources of
overhead. However, pilots were consistently slower than batch for the same
number of average workers. This is particularly visible in Configuration 4
on B\'eluga (Fig. \ref{fig:mwbeluga}), and in Configuration 2, 3 and 4 on
Cedar (Fig. \ref{fig:mwcedar}). It means that some sort of overhead
impacted pilots but not batch. It can also be noticed that both batch and
pilots occasionally deviated from the model line, in particular
Configurations 2 and 3 in B\'eluga: this is due to the fact that our
application is not a divisible load, as the model assumes. Extending the
model beyond divisible loads is easy enough for batch and confirms that the
observed deviations from the model line come from this assumption (see gray
line in Fig.~\ref{fig:mwall}). The extended expression for pilots is more complex
though.
